---
output: github_document
---

tabler: quick and simple regression tables
====================

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

The `tabler` package offer a quick way to make nicely-formatted tables of
multiple regression models. This is not meant to have all of the customizability
of other packages like
[stargazer](https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf)
or [estout](https://cran.r-project.org/web/packages/estout/estout.pdf), and it
currently exports to spreadsheet format (csv or xls/xlsx) only. However, it
provides a convenient way to quickly convey results when shared amongst
collaborators.

Installation and Documentation
------------

`tabler` is still under active development and testing and has not yet been
submitted to CRAN.

You can install the development version of the `tabler` package using [devtools](https://github.com/hadley/devtools):

```
library(devtools)
install_github("robertgambrel/tabler")
```

Please let me know about any problems by [opening an issue](http://github.com/robertgambrel/tabler/issues).

Usage
------------
```{r}
library(tabler)

lm1 <- lm(mpg ~ cyl, data = mtcars)
lm2 <- lm(mpg ~ hp, data = mtcars)
lm3 <- lm(mpg ~ cyl + hp, data = mtcars)

tablify(lm1, lm2, lm3)
tablify(lm1, lm2, lm3, cutoffs = c(0.05, 0.01, 0.001))

```

For more examples on how to use some of the functionality, check out the Vignettes.

```
browseVignettes(package="tabler")
```


Limitations
----------

Since this package relies on
[`broom`](https://cran.r-project.org/web/packages/broom/index.html) to tidy
model outputs into the columns for tables, it is currently limited to model
types handled by broom. For the latest list, [see the developer's
site](https://github.com/dgrtwo/broom#available-tidiers). Most frequently-used
models should be handled, though.
