---
title: "An Introduction to tabler"
author: "Robert J. Gambrel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette will show a few examples of how to use this package and alter what
is output. It will also highlight some restrictions on formats that the user can
request.

## Default values

The main function used from this package is `tablify`. This function accepts a 
series of model output objects as its main arguments, converts the outputs to 
dataset columns (using the `tidy` function from the `broom` package), and then
outputs two objects:

  - A cleaned dataset where each column contains one model and each row contains
  regression results
  - A string caption that explains the values of significance stars in the model
  
```{r}
library(tabler)

lm1 <- lm(mpg ~ wt, data = mtcars)
lm2 <- lm(mpg ~ wt + cyl, data = mtcars)

tablify(lm1, lm2)
```

If the user wants to manually manipulate the dataset of regression output:

```{r}
start_table <- tablify(lm1, lm2)[[1]]
```

In general, the internal R object output is meant to be intermediary, or used as a preview before exporting the table to share. Exporting is achieved by:

```{r, eval = F}
library(WriteXLS)
tablify(lm1, lm2, file = "myresults.csv")
tablify(lm1, lm2, file = "myresults.xls")
tablify(lm1, lm2, file = "myresults.xlsx")
```

Outputs to `xls` or `xlsx` formats requires the `WriteXLS` package.


## Customizing Outputs

The default output can be altered in several ways:

- `teststat`: by default is `"p.value"`, but can also be `"std.error"` or `"statistic"`
  - `"statistic"` will be a t-value or z-value and is model-dependent
- `digits`: by default is 3, and specifies the number of decimal rounding places
  - `digits_coef` and `digits_teststat` take on the `digits` value, unless they are explicitly specified. These allow more control over rounding coefficient vs. significance test outputs
- `cutoffs`: by default `c(0.1, 0.05, 0.01)`, these specify the cutpoints at which significance markers are displayed. They must be presented in decreasing order, and any number are allowed.
- `stars`: by default `c("*", "**", "***")`, this list must be the same length as `cutoffs` and again in order of weakest significance to strongest significance
- `intercept_last`: by default `TRUE`, moves the intercept output to the bottom of the table (but before observation count and model fit statistics). If `FALSE`, reports it first.
- `N`: by default `TRUE`, adds a row to the table displaying observation count
- `fit`: by default `NULL`, can also be a string or list of fit statistics available in a regression output ("r.squared", "adj.r.squared")
- `file`: by deafult `NULL`, specifies the output file name and path if desired

```{r}
lm3 <- lm(mpg ~ cyl + disp + hp + drat + wt + qsec + vs, data = mtcars)
tablify(lm3)
tablify(lm3, cutoffs = c(0.2, 0.1, 0.05))

# error:
# tablify(lm3, cutoffs = c(0.9, 0.7, 0.5, 0.3, 0.1))

# correct - must supply enugh significance denoters
tablify(lm3, cutoffs = c(0.9, 0.7, 0.5, 0.3, 0.1), 
        stars = c('?', '+', '*', '**', '***'))

tablify(lm1, lm2, lm3, fit = c("r.squared", "adj.r.squared"))
```

## Final note on model types

Since this package relies on
[`broom`](https://cran.r-project.org/web/packages/broom/index.html) to tidy
model outputs into the columns for tables, it is currently limited to model
types handled by broom. For the latest list, [see the developer's
site](https://github.com/dgrtwo/broom#available-tidiers). Most frequently-used
models should be ready to go, though.

Models of different types (i.e. OLS and ordinal / binary logit) can be combined
into one table, so long as the requested outputs are common between all of them.
For example, requesting coefficients and their p-values will work, but
requesting $R^2$ will fail, as ordinal models do not include this in their
outputs.
